Introduction

### 2020-09-21 text/introduction.Rmd
add hotnet2 reference

More recently, pan-cancer mutations and other data have been looked at as
disruptions of normal pathway activity. @PCAWG-PATH carried out exhaustive
analysis of pathway enrichment using whole genome data. Network approaches
address the sparseness of mutations, allowing genes to be influenced by
mutations in nearest network neighbors [@hornNetSigNetworkbasedDiscovery2018;
@Iranzo-Network]. These methods are powerful especially when applied to smaller
numbers of tumors. One of the challenges in the field remains that there may be
thousands of moderate effect genes that occur at such low frequency--given
tissue diversity and low sample number--that they are impossible to detect using
positive selection theory. Some groups have attempted to address this challenge
by applying machine learning to cancer data to discover groups of
functionally related genes as they interact with larger pathways and networks
[@kimPancancerAnalysisSomatic2018;
@mourikis-ml-pathways; @moonlight]. These studies have proven very effective at
highlighting fundamental disease phenotypes at the pathway level across cancers
with different origins at the cellular and tissue level.

>>>>

More recently, pan-cancer mutations and other data have been looked at as
disruptions of normal pathway activity. @PCAWG-PATH carried out exhaustive
analysis of pathway enrichment using whole genome data. Network approaches
address the sparseness of mutations, allowing genes to be influenced by
mutations in nearest network neighbors [@hotnet2;@hornNetSigNetworkbasedDiscovery2018;
@Iranzo-Network]. These methods are powerful especially when applied to smaller
numbers of tumors. One of the challenges in the field remains that there may be
thousands of moderate effect genes that occur at such low frequency--given
tissue diversity and low sample number--that they are impossible to detect using
positive selection theory. Some groups have attempted to address this challenge
by applying machine learning to cancer data to discover groups of
functionally related genes as they interact with larger pathways and networks
[@kimPancancerAnalysisSomatic2018;
@mourikis-ml-pathways; @moonlight]. These studies have proven very effective at
highlighting fundamental disease phenotypes at the pathway level across cancers
with different origins at the cellular and tissue level.
